### 2019-04-01 Thesis/games.tex
Nightly commit.

@@

  Then, for any objects $A,B$ of $\C$, there is a natural sequence
  \[
    B \leftarrow B\tensor A \leftarrow B\tensor A^2 \leftarrow B \tensor A^3 \leftarrow \cdots\,.
    \]
  In particular, there is a sequence
  \[
    I \leftarrow A \leftarrow A^2 \leftarrow A^3 \leftarrow \cdots\,.
    \]
  Suppose that this sequence has a limit $\oc A$, and that $B\tensor \oc A$ is the limit of the first sequence for all $B$.  
  Then $\oc A$ has the structure of the cofree commutative comonoid on $A$.
  \label{TheMtt}
\end{theorem}

@@

@@

                  \&[18pt] I \tensor \oc\V_\Gamma \arrow[dd, "\oc\deno{s\vert_x}\tensor\oc\V_\Gamma" description, thick] \\

@@

>>>>

Note also that if $m,n$ are integers, then any permutations $\sigma$ of $1,\cdots,m$ and $\pi$ of $1,\cdots,n$ induce a permutation $[\sigma,\pi]$ of $1,\cdots,m+n$.  
Then we get morphisms
\[
  A^{m+n} \to A^{\tensor (m+n)} \to A^{\tensor m} \tensor A^{\tensor n}\,,
  \]
which are equalized by all symmetries on $A^{\tensor m}$ and $A^{\tensor n}$ individually.  
Since the equalizers $A^m$ and $A^n$ are preserved by the tensor product, then we get an induced morphisms
\[
  A^{m+n}\to A^m\tensor A^n\,.
  \]

@@

  Then, for any objects $A,B$ of $\C$, there is a natural sequence
  \[
    B \leftarrow B\tensor A \leftarrow B\tensor A^2 \leftarrow B \tensor A^3 \leftarrow \cdots\,.
    \]
  In particular, there is a sequence
  \[
    I \leftarrow A \leftarrow A^2 \leftarrow A^3 \leftarrow \cdots\,.
    \]
  Suppose that this sequence has a limit $\oc A$, and that $B\tensor \oc A$ is the limit of the first sequence for all $B$.

  For each $m$, we can define morphisms
  \[
    \oc A \to A^{m+n} \to A^m \tensor A^n
    \]
  for each $n$, which commute with the morphisms $A^{n+1}\to A^n$ and hence induce a morphism $\oc A \to A^m \tensor \oc A$.  
  Then these morphisms themselves commute with the morphisms $A^{m+1}\tensor \oc A \to A^m \tensor \oc A$, and so we get a morphism $\mu_A\from \oc A \to \oc A \tensor \oc A$.

  The morphisms $\mu_A\from \oc A \to \oc A \tensor \oc A$ and $()\from A \to I$ give $\oc A$ the structure of a commutative comonoid in $\C$.  
  In fact, this is the \emph{cofree commutative comonoid} over $A$ in $\C$.  
  The counit $\der_A\from \oc A \to A$ of the adjunction is the map in the limiting cone.
  \label{TheMtt}
\end{theorem}

@@

One small thing we need to do is to relate the two structures on the exponential.

\begin{proposition}
  The final coalgebra
  \[
    \alpha\from \oc A \to A \sequoid \oc A
    \]
  is given by the composite
  \[
    \oc A \xrightarrow{\mu_A} \oc A \tensor \oc A \xrightarrow{\der_A\tensor \oc A} A \tensor \oc A \xrightarrow{\wk_A,\oc A} A \sequoid \oc A\,.
    \]
  \label{PropFormulaForAlpha}
\end{proposition}
\begin{proof}
  By Theorem \ref{TheMtt}, we can tell that this composite is a copycat strategy between $\oc A$ and $A \sequoid \oc A$, as is $\alpha$.  
  Since $A$ is well-opened, there is a unique such strategy.
\end{proof}

@@

                  \&[17pt] I \tensor \oc\V_\Gamma \arrow[dd, "\oc\deno{s\vert_x}\tensor\oc\V_\Gamma" description, thick] \\

@@

      Now we have a commutative diagram
      \begin{figure}[htbp]
        \[
          \begin{tikzcd}[column sep=41pt, row sep=30pt]
            I \arrow[r, "\oc s(x)"] \arrow[d, "\oc n" description] \arrow[dr, Rightarrow, no head]
              & \oc \bN \arrow[r, "\cell"] \arrow[d, "()" description] \arrow[dr, "\cell_0" description]
                & \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[dd, "\alpha_{\Varr}" description, controls={+(1,-0.25) and +(0.8,0.75)}, start anchor={[yshift=-1pt]}, end anchor = {[xshift=25pt]}]
                  & \oc \Varr \tensor \oc \Varr \arrow[d, "\der_{\Varr} \tensor \oc\Varr" description]  \\
            \oc\bN \arrow[dd, "\cell" description] \arrow[ddr, "\lunit_{\oc\bN}" description, end anchor={[xshift=-3pt, yshift=-2pt]}]
              & I \arrow[l, "\oc n" description]
                & \Varr \sequoid \oc\bN \arrow[d, "\Varr\sequoid\cell" description] \arrow[dd, "\pr_n\sequoid\oc\bN" {description, pos=0.44}, controls={+(-2.5,-0.2) and (-0.5,0.5)}]
                  & \Varr \tensor \oc\Varr \arrow[dl, "{\wk_{\Varr,\oc\Varr}}" description] \arrow[dd, "\pr_n\tensor\oc\Varr" description] \\
            %
              & \bC \tensor \oc\bN \arrow[dr, "{\wk_{\bC,\oc\bN}}" description] \arrow[ddr, "\bC \tensor \cell" description]
                & \Varr \sequoid\oc\Varr \arrow[ddr, "\pr_n\sequoid\oc\Varr" description]
                  & \\
            \oc\Varr \arrow[d, "\mu_{\Varr}" description] \arrow[dr, "\lunit_{\oc\Varr}" description]
              & I \tensor \oc\bN \arrow[u, "\skipp\tensor\oc\bN" {description, pos=0.44}] \arrow[d, "I\tensor \cell" description]
                & \bC \sequoid \oc\bN \arrow[dr, "\bC \sequoid \cell" description]
                  & \bC \tensor \oc\Varr \arrow[d, "{\wk_{\bC,\oc\Varr}}" {description, pos=0.44}] \\
            \oc\Varr \tensor \oc\Varr \arrow[r, "()\tensor\oc\Varr"']
              & I \tensor \oc\Varr \arrow[r, "\skipp \tensor \oc\Varr"']
                & \oc\bC \tensor \oc\Varr \arrow[r, "{\wk_{\bC,\oc\Varr}}"']
                  & \bC \sequoid \oc\Varr
          \end{tikzcd}
          \]
      \end{figure}
  \end{itemize}
\end{proof}
